\documentclass[letterpaper,11pt]{article}

\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}[section]

\begin{document}
\noindent{COSC 302: Analysis of Algorithms --- Spring 2018}

\noindent{\bf Problem Set 7 --- Minimum Spanning Trees and Single Source Shortest Paths} 
\noindent {\bf Due by 4:30pm Friday, March 30, 2018 as a single pdf via Moodle (either generated via \LaTeX{}, or concatenated photos of your work). Late assignments are not accepted.} 

This is an \emph{individual} assignment: collaboration (such as discussing problems and brainstorming ideas for solving them) on this assignment is highly encouraged, but the work you submit must be your own. Give information only as a tutor would: ask questions so that your classmate is able to figure out the answer for themselves. It is unacceptable to share any artifacts, such as code and/or write-ups for this assignment. If you work with someone in close collaboration, you must mention your collaborator on your assignment.

\emph{Suggested practice problems, from CLRS:} 23.1-3; 23.1-6; 23.2-4; 23.2-5; 24.1-1

\begin{enumerate}
\item Problem 23.1-1 from CLRS.
Let $G = (V,E)$ be a connected undirected graph. Let $(u,v)$ be a minimum weight edge. Let there be $T$ which is some subset of $E$ that does not contain a vertex $u$. Since $(u,v)$ is a minimum weight edge, it is a safe edge. And a minimum spanning tree must contain all vertices including $v$ the edge $(u,v)$ will be added.
\item Problem 23.2-8 from CLRS.
\\Invariant: $G_1$ and $G_2$ are both subsets of a minimum spanning tree.
\\Maintenance: if $G_1$ and $G_2$ are one vertex, Then add the edge between them that's in $E$. Otherwise, search for an minimum weight edge $(u,v)$ such that $(u,v) \notin E_1$ and $(u,v) \notin E_2$. Recall that both $G_1$ and $G_2$ are subsets of a minimum spanning tree and $(u,v)$ is a light edge. So by Corollary 23.2, a light edge connecting two components that are subsets of a minimum spanning tree is considered safe and thus creates another subset of the tree.
\\Termination: Terminates when $G_1$ and $G_2$ are combined and the result contains all vertices in $V$.
\item Problem 24.1-6 from CLRS. \emph{Hint: Consider running Bellman-Ford more than once.}
\item Problem 24.3-4 from CLRS.

\end{enumerate}

\end{document}
